Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-04-11 journal-draft/ettdoc.tex
author symbol

\definecolor{slightgray}{gray}{.90} 
\usepackage{rotating}
\usepackage{hhline}
\usepackage{float}
\usepackage{caption}% http://ctan.org/pkg/caption
\captionsetup[table]{format=plain,labelformat=simple,labelsep=period}%
%\usepackage{authblk}

@@

\title{Robust Clustering for Ad Hoc Cognitive Radio Network}
%\author[1]{Di Li\thanks{li@umic.rwth-aachen.de}}
%\author[2]{Erwin Fang\thanks{xx}}
%\author[3]{James Gross}
\author{Di Li, Erwin Fang, James Gross\corrauth}
%\affil[1]{RWTH Aachen University}
%\affil[2]{ETH Zurich}
%\affil[3]{KTH Royal Institute of Technology}
\address{RWTH Aachen University, ETH Zurich, KTH Royal Institute of Technology }
%\renewcommand\Authands{ and }
\corraddr{Communication Theory Lab
School of Electrical Engineering, 
KTH Royal Institute of Technology
SE - 100 44 Stockholm\\Email: james.gross@ee.kth.se}

>>>>

\definecolor{slightgray}{gray}{.90} 
\usepackage{rotating}
\usepackage{hhline}
\usepackage{float}
\usepackage{caption}% http://ctan.org/pkg/caption
\captionsetup[table]{format=plain,labelformat=simple,labelsep=period}
%\usepackage{authblk}

@@

\title{Robust Clustering for Ad Hoc Cognitive Radio Network}
%\author[1]{Di Li\thanks{li@umic.rwth-aachen.de}}
%\author[2]{Erwin Fang\thanks{xx}}
%\author[3]{James Gross}
\author{Di Li\textsuperscript{1}, Erwin Fang\textsuperscript{2}, James Gross\textsuperscript{3}\corrauth}
%\affil[1]{RWTH Aachen University}
%\affil[2]{ETH Zurich}
%\affil[3]{KTH Royal Institute of Technology}
\address{RWTH Aachen University\textsuperscript{1}, ETH Zurich\textsuperscript{2}, KTH Royal Institute of Technology\textsuperscript{3} }
%\renewcommand\Authands{ and }
\corraddr{Communication Theory Lab
School of Electrical Engineering, 
KTH Royal Institute of Technology
SE - 100 44 Stockholm\\Email: james.gross@ee.kth.se}
